Fixing Vulnerabilities Hinders Maintainability

### 2019-01-30 paper/ICPC19/icpc19.tex
abstract + title

\title{Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code}

@@

\begin{abstract}
Nowadays, security is an absolutely necessary requirement for the production of quality software. However, there is still a considerable amount of zero-day vulnerabilities published and fixed almost every week. The authors suspect that when developers address these vulnerabilities on their codebases, they actually affect the maintainability of software and even introduce more vulnerabilities. This paper evaluates the impact of refactorings to improve security on the maintainability of open-source software. Maintainability is measured based on the \emph{Better Code Hub}'s model of 10 guidelines for both before and after security commits for a dataset including 607 security commits. Results show that fixing software vulnerabilities harms the maintainability of open-source software. Specially for refactorings that deal with \emph{Broken Authentication and Session Management}, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. Therefore, it is necessary to bring awareness for coding good practices and for the use of automated tools that have the potential to help developers with this issue.
\end{abstract}

>>>>

\title{Fixing Vulnerabilities Hinders Maintainability}

@@

\begin{abstract}
Security is a requirement of utmost importance to produce software with high
quality. However, there is still a considerable amount of zero-day
vulnerabilities being discovered, and fixed, almost weekly. We suspect that when
developers address these vulnerabilities on their codebases, they actually
affect the maintainability of software, potentially introducing other
vulnerabilities. This paper evaluates the impact of refactorings to improve
security on the maintainability of open-source software. Maintainability is
measured based on the \emph{Better Code Hub}'s model of 10 guidelines using a
dataset including $607$ security commits. Results show that fixing software
vulnerabilities hinders the maintainability of open-source software. This is
particularly the case for refactorings that address \emph{Broken Authentication
and Session Management}, \emph{Memory Leaks} and \emph{Denial-of-Service}
attacks. Therefore, it is necessary to bring awareness for coding practices and
for the use of automated tools that have the potential to help developers with
this issue.
\end{abstract}
